Races with hyper3 objects

### 2022-06-27 inst/race3.Rmd
more likelihood functions

>>>>

## Results for AAAB

```{r,plotaaab,cache=TRUE}
Hab <- function(i,n=4){
  jj <- rep("a",n)
  jj[i] <- "b"
  ordervec2supp3(jj)
}

small <- 1e-5
a <- seq(from=small,to=1-small,len=400)

plot(0:1,c(0,1),type="n",xlab="p[a]",ylab="likelihood")
dop <- function(w, n, ...){
  Hjj <- Hab(w,n)
  y <- sapply(a,function(p){loglik(c(a=p,b=1-p),Hjj,log=FALSE)})
  points(a,y/max(y),type="l",...)
}
dop(1,4,col="black")
dop(2,4,col="red")
dop(3,4,col="blue")
dop(4,4,col="green")
```

```{r,plotaaaaaaab,cache=TRUE}
plot(0:1,c(0,1),type="n",xlab="p[a]",ylab="likelihood")
for(i in 1:10){dop(i,10,col=rainbow(10)[i])}
```

```{r,plot40ab,cache=TRUE}
plot(0:1,c(0,1),type="n",xlab="p[a]",ylab="likelihood")
for(i in 1:40){dop(i,40,col=rainbow(40)[i])}
```
